--- 
title: 'Researcher Development Program Mentors'
output:
    tufte::tufte_html
--- 
```{r set_knitr_chunk_options, echo=FALSE, message=FALSE}
#set global output chunk options
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, collapse = F, highlight = F, results = "asis")
```

```{r}
library(tidyverse)
library(ggrepel)
library(kableExtra)
library(janitor)
library(leaflet)
library(readxl)
```

```{r}
#import data 
mentor20 <- read_csv("2020_RDP_Mentors.csv")
mentor21 <- read_csv("2021_RDP_Mentors.csv")
geocode <- read_xlsx("College_Geocodes.xlsx")
```

```{r}
# Get the unique institutions 
institutions <- union(mentor20, mentor21)

#Made another dataset with more rdp mentor intstitions 
rdp <- read_xlsx("RDP_institutions.xlsx")
```

```{r}
#Only get names in the geocodes data that are in the institutions data set
df <- geocode %>% 
  filter(NAME %in% rdp$Institution)

#match rdp colleges by unitid column 
df <-geocode %>% 
  filter(UNITID %in% rdp$UNITID)

# See if there are any rows missing
#anti_join(rdp, df, by = c("Institution" = "NAME"))
```
---
# RDP Mentors

RDP is thankful for the many mentors who have spent countless hours pouring into graduate students. Our mentors help guide and teach RDP mentees the ins and outs of research methods. Many of our mentors come from across the United States and beyond. 

This map shows some of the locations of current and former RDP mentors. If you hover over the markers, you will see which institution our mentors represent. 

```{r}
df %>% 
leaflet() %>%
addProviderTiles(providers$Esri.WorldImagery, group = "World Imagery") %>%
addProviderTiles(providers$CartoDB.Positron, group = "Carto") %>% 
addProviderTiles(providers$Stamen.TonerLite, group = "Toner Lite") %>%
addLayersControl(baseGroups = c("Toner Lite", "Carto", "World Imagery")) %>%
addMarkers(label = df$NAME)

```


